---
title: "allison_day_6"
author: "Risa Lewis"
date: "9/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
library(RColorBrewer)
library(ggbeeswarm)
library(stargazer)
```

### Read in lobster data

```{r}
lobsters <- read_csv(here("data", "lter_lobster.csv")) %>% 
  clean_names()
```
### Make a copy

```{r}
lobster_eda <- lobsters
```

### A couple different visualizations

#### Histograms

```{r}
lobster_eda <- lobster_eda %>% 
  uncount(count)

ggplot(data = lobster_eda, aes(x = size)) +
  geom_histogram() +
  labs(x = "Lobster carapace length (mm)",
       y = "Frequency",
       title = "Lobster size distribution")
```


### Quantile-Quantile plot to explore normality

```{r}
ggplot(data = lobster_eda, aes(sample = size)) +
  geom_qq() +
  facet_wrap(~ site)
```

#### Boxplot

```{r}
ggplot(data = lobster_eda, aes(x = site, y = size)) +
  geom_boxplot(aes(fill = site)) +
  labs(x = "Study site",
       y = "Lobster size (mm)",
       title = "Lobster sizes, SB Coast") +
  theme_minimal()
```


#### Jitter plot

```{r}
ggplot(data = lobster_eda, aes(x = site, y = size)) +
  geom_jitter(width = 0.1, alpha = 0.4, size = 0.7) +
  geom_boxplot(alpha = 0.2)
```


#### Beeswarm Plot

```{r}
ggplot(data = lobster_eda, aes(x = site, y = size)) +
  geom_beeswarm() +
  geom_violin(aes(fill = site), alpha = 0.5) +
  facet_wrap(~ site)
```

#### Summary Stats

```{r, echo = TRUE}
count_by_site <- lobster_eda %>% 
  count(site, year)

lobster_summary <- lobster_eda %>% 
  group_by(site) %>% 
  summarize(mean_size = mean(size),
          sd_size = sd(size))
```

#### Hypothesis Testing

```{r}
sample_1 <- c(2,5,4,3,5,6,7,7,9)
sample_2 <- c(10,9,6,12,18,11,5,2,14)

example_ttest <- t.test(sample_1, sample_2)
example_ttest
```

### How to make your own data frame

```{r}

df <- dplyr::tribble(
  ~teddy, ~allison, ~greg,
  1, 2, 3,
  10, 12, 15
  )
```

### Linear Regression

Using the 'trees' built-in dataset.

```{r}
ggplot(data = trees, aes(x = Girth, y = Volume)) +
  geom_point() +
  geom_smooth(method = "la")
```

#### Model Linear Relationship

```{r}
tree_lm <- lm(Volume ~ Girth, data = trees)

tree_lm

summary(tree_lm)

plot(tree_lm)
```

My formula is $y = mx + b$

#### Multiple linear regression

```{r}
tree_mlr <- lm(Volume ~ Height + Girth, data = trees)

tree_mlr

plot(tree_mlr)
```
### Summary Output Table

```{r, results = "asis"}
stargazer(tree_mlr, type = "html")
```

